---
title: "intro of functions"
author: "By SA23204156 程张伟"
date: "2023-12-04"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro of functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview  
   
__SA23204156__ is a simple R package of two functions.The ellipse.general function can draw a confidence ellipse.The maxcol function can calculate the maximum module length of each column in the matrix.The ellipse.general function is a R function, while the maxcol function is a Rcpp function.
   
## Example of f1 function  
  
```{r,eval=FALSE}
library(ggplot2)
library(Rcpp)
```


```{r,eval=FALSE}
ellipse.general <- function(mu, s, c){
  ellipse.simple <- function(s1, s2, c){
    a <- s1*c
    b <- s2*c 
    x <- seq(from = -a, to = a, length.out = 400)
    points <- data.frame(
      x1 = c(-x, x),
      x2 = NA
    )
    points$x2[1:400] <- sqrt(((a*b)^2-(b*x)^2)/a^2)
    points$x2[401:800] <- -sqrt(((a*b)^2-(b*x)^2)/a^2)
    return(points)
  }
  lambda <- diag(eigen(s)$values)  # 特征值
  P <- eigen(s)$vectors            # 特征向量
  Y <- ellipse.simple(s1 = sqrt(lambda[1,1]), s2 = sqrt(lambda[2,2]), c = c)  
  X <- t(P%*%t(Y) + mu)  # 对坐标旋转位移
  X <- as.data.frame(X)
  colnames(X) <- c('x1', 'x2')
  return(X)
}
```

```{r,eval=FALSE}
# 设置参数
mu <- c(2.5, 2.5)  # 均值向量
s <- matrix(c(2, 1, 1, 2), ncol = 2)  # 协方差矩阵
c <- 1
# 计算坐标
X <- ellipse.general(mu = mu, s = s, c = c)
ggplot(
  data = X,
  mapping = aes(x = x1, y = x2)
) +
  geom_path() +
  geom_hline(yintercept = 0,lty = 2) +
  geom_vline(xintercept = 0, lty = 2)
```
   
In this example, the mu is the mean vector of binary normal, while the s is the covariance matrix of binary normal.As the picture drawing with ggplot2, we can see the points we generate with our function.It is really a true confidence ellipse.


    
## Example of f2 function  
   
```{r,eval=FALSE}
cppFunction(' double maxcol(NumericMatrix x){
   int nr = x.nrow();
   int nc = x.ncol();
   double y, yl;
   y = 0.0;
   NumericVector ycol(nr);
   for(int j = 0; j < nc; j++){
     ycol = x.column(j);
     yl = sum(ycol * ycol);
     if(yl > y) y = yl;
   }
   y = sqrt(y);
   return y;
 }')
X <- matrix(rnorm(100*100), nrow = 100, ncol = 100)
a <- maxcol(X)
a
```

In this example, the X is a random matrix generated from normal distribution. With the f2 function, we can easily get the maximum module length of each column in the matrix. 